% !TeX root = cv.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% tungufoss Resume/CV
% XeLaTeX Template
% Version 1.0 (30/01/15)
%
% This template was based on Friggeri Resume/CV 
% by Adrien Friggeri https://github.com/afriggeri/CV
% and updated by Helga Ingimundardottir https://github.com/tungufoss/cv
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{references.bib} % Specify the bibliography file to include 
%publications

\begin{document}

\header{Dr.\;Helga}{Ingimundard\'{o}ttir}{Ph.D. in computational engineering} % Your name and 
%current job title/field

%-------------------------------------------------------------------------------
%	SIDEBAR SECTION
%-------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
%\address{Taeknigardur, \mbox{Office \#217}}{Dunhaga 5}{Reykjavik IS-107}{Iceland}
\address{Helga Ingimundardóttir}{Kinnargata 6}{Gardabaer IS-210}{Iceland}
~
\mobile{(+354) 865 1341}
%\phone{(+354) 525-4704}
~
\email{tungufoss@gmail.com}
%\homepage{https://notendur.hi.is/hei2}{www.hi.is/$\sim$hei2}
\twitter{tungufoss}
\github{tungufoss}
\facebook{helga.ingimundardottir}
\linkedin{helgaingimundardottir}
\orcid{0000-0002-2780-3546}
\section{languages}
Icelandic mother tongue
English fluency
Danish conversational
French conversational
\section{programming}
\entryaside{All-purpose}{C$\#$, C++, Python}
\entryaside{Numerical}{MATLAB}
\entryaside{Statistical}{R, tidyverse}
\entryaside{SQL}{Microsoft SQL Server, PostgreSQL}
\entryaside{Optimisation}{GLPK, Gurobi}
\entryaside{Scripting}{awk, grep, sed, make}
\end{aside}


\section{education}
%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{2009--2016}
{Ph.D. {\normalfont of Computational Engineering}}
{The University of Iceland, Reykjavik}
{Conducted research on hyperheuristics with guidance from Prof. Tómas Philip Rúnarsson. Focused on automating the scheduling process for Job Shop Scheduling Problems using ordinal regression and analyzed the ``problem difficulty'' and ``algorithm's footprints in instance space'' for such optimization problems. Awarded a doctoral grant from the University of Iceland Research Fund. \\
{\boldfont Thesis:} \emph{ALICE: Analysis \& Learning Iterative Consecutive Executions}. Available at \url{http://hdl.handle.net/1946/25337}.}
%------------------------------------------------
\entry
{2010--2012}
{Graduate Diploma {\normalfont of School of Education}}
{The University of Iceland, Reykjavik}
{Teaching Studies for Higher Education.}
%------------------------------------------------
\entry
{2008--2010}
{Masters {\normalfont of Computational Engineering}}
{The University of Iceland, Reykjavik}
{Conducted research with Prof. Sylvain Lalot at the Université polytechnique Hauts-de-France in Valcencinnes, France. Explored the feasibility of using wavelet transforms to detect fouling in cross-flow heat exchangers using measurements obtained during normal operation.
Awarded a grant from the Icelandic French Embassy to study in France. \\	
{\boldfont Thesis:} \emph{Detection of Fouling: Effectiveness Ratio Method}. Available at \url{http://hdl.handle.net/1946/4445}.}
%------------------------------------------------
\entry
{2005--2008}
{Bachelor {\normalfont of Mathematics}}
{The University of Iceland, Reykjavik}
{Specialization in Computer Science}
%------------------------------------------------
\end{entrylist}


\section{interests}
%-------------------------------------------------------------------------------
%	INTERESTS SECTION
%-------------------------------------------------------------------------------
{\boldfont professional:} heuristics, artificial intelligence, evolutionary 
computation, global optimisation, statistical learning, machine learning, big data, automation, data visualisation and real world applications 

{\boldfont personal:} knitting, sewing, general arts and crafts, horticulture,  podcasting, internet cats and Russian Blues



\section{work experience}

%-------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------

\begin{entrylist}
\entry
{2022--23}
{Travelshift}
{Reykjavik, Iceland}
{\emph{Head of AI research} at
	\href{https://www.travelshift.com/}{Travelshift}.\\
As the leader of an AI research team, I developed and implemented data-driven approaches to optimize travel plans for vacation packages offered on \href{www.guidetoeurope.com}{GuideTo\-Europe.com}. Our project focused on the NP-hard optimization problem of the traveling thief, which combines the concepts of the knapsack problem and the traveling salesman problem. 
In addition, I worked on patent applications related to our research.
I ensured that the optimized travel plans met stakeholders' requirements by designing and implementing AI algorithms, analyzing data, collaborating with other teams, and staying up-to-date with AI research trends and advancements.}
\end{entrylist}

\clearpage
\removeaside

\begin{entrylist}
%------------------------------------------------
\entry
{2015, 2023--}
{RANNIS}
{Reykjavik, Iceland}
{\emph{Contractual Advisor} in 
	\href{http://www.rannis.is/sjodir/rannsoknir/taeknithrounarsjodur/fagrad/}{Technology
		Development Fund}\\
	I served on the advisory board for grant applications to the Technology Development Fund at RANNIS in 2015 and provided valuable insights on the selection of R\&D projects for technological development and innovation in Iceland. 
	I resumed my role as an advisor in 2023.
}
%------------------------------------------------
\entry
{2021--2022}
{CCP Games}
{Reykjavik, Iceland}
{\emph{Data Scientist} for
	\href{https://www.ccpgames.com/}{CCP Games}' data department.\\
I played a leading role in the development of a recommendation engine service for new characters in EVE Online, working alongside other partners. My responsibilities included creating real-time time-series features based on proto-events from Redis or Kafka streams, using the TimescaleDB extension for pgSQL functions for feature engineering. Additionally, I developed ad-hoc metrics to measure content quality and engagement for these new recommendation models.
}
%------------------------------------------------
\entry
{2016--2021}
{deCODE Genetics}
{Reykjavik, Iceland}
{\emph{Research Scientist} for
    \href{https://www.decode.com/}{deCODE}'s statistical department.\\
    I implemented and maintained the Oxford Nanopore Technologies long range sequencing analysis pipeline for deCODE. This involved working closely with the lab department to decide on protocols and collaborating with the ITO to make necessary changes to cluster and disk architecture to efficiently process the large amount of data (6 petabytes over 3 years) while ensuring data integrity. 
}
%------------------------------------------------
\entry
{2015--2016}
{AGR Dynamics}
{Reykjavik, Iceland}
{\emph{SQL Consultant} for
    \href{http://agrdynamics.com/}{AGR 5}\\
As a SQL consultant for AGR 5, a web-based supply chain management system, I provided customized solutions to meet individual customer needs. Working on the system's back-end, I implemented data and maintained databases. In addition, I developed custom SQL solutions for specific customer requirements. AGR 5 allows users to visualize sales history and generate order proposals using statistical forecasting.
}    
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{2013--2015}
{VALKA}
{Kopavogur, Iceland}
{\emph{Computational Engineer} in Research and Development \\
As a full-time researcher at Valka, a leading provider of equipment and automation solutions for the fish processing industry, I played a crucial role in several important accomplishments. These include designing and implementing an intelligent fish portioning algorithm based on X-Ray imagery, generalizing the fish bone detection algorithm for multiple species with fast and accurate calculations, collaborating on three-dimensional visualizations of fish bones, and conducting efficiency tests and preparing reports. Through these achievements, I helped to contribute to Valka's success in delivering innovative solutions to the industry.
}
%------------------------------------------------
%\entry
%{2007--2009}
%{LANDSBANKINN}
%{Reykjavik, Iceland}
%{\emph{Summer Intern} at: Testing Department in 2009; Quantitative Research and Trading Support for the FX and Derivatives Sales in 2008; and at Business Support in 2007.}
%------------------------------------------------
\end{entrylist}
%------------------------------------------------

\section{academic experience}
%-------------------------------------------------------------------------------
%	ACADEMIC EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}
    \entry
	{2023}
	{University of Iceland, Industrial Engineering Department}
	{Reykjavik Iceland}
	{\emph{Sessional Teacher} in Business Intelligence (\href{https://ugla.hi.is/kennsluskra/index.php?tab=nam&chapter=namskeid&id=71001420230}{IDN610M}). \\
As a lecturer for the Business Intelligence course, I taught 3rd year BSc and 1st year MSc students the practical applications of supervised learning, clustering, and process mining using real-world data. My project-driven approach and emphasis on active participation helped students develop practical skills such as effective use of GitHub and technical report writing. By the end of the course, students gained a solid understanding of key machine learning techniques and their use cases, preparing them for success in their future careers.
	}
\end{entrylist}
\begin{entrylist}
    %------------------------------------------------
    \entry
    {2011--2012}
    {University of Iceland, Industrial Engineering Department}
    {Reykjavik Iceland}
    {\emph{Sessional Teacher} in Operations Research (\href{https://ugla.hi.is/kennsluskra/index.php?sid=&tab=nam&chapter=namskeid&id=08213020110}{IDN401G})\\
    As the sole instructor, I took pride in teaching the undergraduate course on Operations Research during the spring semesters of 2011 and 2012. I worked diligently with Gudrun Geirsdottir at the School of Education to restructure the course, including assignments, grading, and tests.\\
    I am particularly proud of my efforts in innovating the course design, assessment, and evaluations of tutorials, which resulted in inspiring a fellow teacher in Natural Sciences. Together, we were able to secure a teaching grant from the University to further develop our methods, and I was honored to have played a part in that success.\\
    Overall, I am pleased with the work I did in the course and the grant we received, as they are testaments to my dedication to teaching and my ability to think creatively and collaboratively to achieve positive outcomes.
    }

    %------------------------------------------------
    \entry
    {2007--2010}
    {University of Iceland, Industrial Engineering Department}
    {Reykjavik Iceland}
    {\emph{Teaching Assistant}, School of Engineering and 
    Natural Sciences \\
        Worked as a tutor during tutorials, correcting and working through 
        handouts for the following under graduate courses: 
        \begin{itemize}
            \item Linear Algebra 		\hfill Autumn~2007
            \item Simulations			\hfill Spring~2008
            \item Operational Research 	\hfill Spring~2008
            \item Calculus IB			\hfill Autumn~2009
            \item Numerical Analysis 	\hfill Spring~2010
        \end{itemize}	
    }
\end{entrylist}   

\section{communication skills}
%-------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}
\entry{2022}{Panelist}{3rd European Language Resource Coordination (ELRC) workshop in Iceland}{
As a panelist at the \href{https://lr-coordination.eu/iceland3rd}{third Icelandic ELRC workshop}, I discussed the impact of Language Technology and AI on the Icelandic language with other developers, integrators, and users. We explored the potential of Language Technology to transform digital interactions in both private and public sectors and shared our experiences and perspectives on its current status and future prospects. The discussion was engaging and provided valuable insights into the role of Language Technology in shaping our multilingual future.
}%----------------------------------
\entry{2017-2020}{Podcast host, \href{https://www.storytel.com/is/is/series/28703-Iskisur}{ÍSKISUR}}{Alvarpið \& Storytel}{An Icelandic podcast with three friends who read all 47 books in The Legend of the Ice People series by Margit Sandemo. I curated a segment on Internet cats at the end of each episode. Originally published by Alvarpið from 2017-2018 but moved over to Storytel Iceland in March 2019.
}%------------------------------------------------
\entry
{2016}
{Oral Presentation}
{PhD defence 30th of June at Háskóla Íslands, Reykjavík, Iceland.}
{Presented my PhD thesis \emph{ALICE: Analysis \& Learning Iterative 
Consecutive Executions}. 
Opponents: Prof. Edmund Burke and Prof. Kate Smith-Miles.}
%------------------------------------------------
\entry
{2015}
{Oral Presentation}
{9th Int'l Conference on Learning and Intelligent Optimization (LION9)}
{Presented the paper \emph{ Generating Training Data for Supervised Learning 
Linear Composite Dispatch Rules for Scheduling}, Lille, France.}
%------------------------------------------------
\entry
{2012}
{Oral Presentation}
{6th Int'l Conference on Learning and Intelligent Optimization (LION6)}
{Presented the paper \emph{ Determining the Characteristic of Difficult Job 
Shop Scheduling Instances for a Heuristic Solution Method}, Paris,  France.}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{2011}
{Oral Presentation}
{\mbox{11th Int'l Conference on Intelligent Systems Design \& Applications (ISDA)}}
{Presented the paper  \emph{Sampling Strategies in Ordinal Regression for 
Surrogate Assisted Evolutionary Optimization}, Cordoba, Spain.}
%------------------------------------------------
\entry
{2010}
{Oral Presentation}
{5th Int'l Conference on Learning and Intelligent Optimization (LION5)}
{Presented the paper \emph{Supervised Learning Linear Priority Dispatch Rules 
for Job-Shop Scheduling}, Rome, Italy}
%------------------------------------------------
\entry
{2010}
{Invited speaker}
{Silisian University, Gliwice, Poland}
{I was invited by Prof. Waldemar Grzechca to come to Politechnika Śląska in Gliwice, Poland, as part of the Erasmus+ Teaching Staff Mobility Progamme. During my stay, I presented my Ph.D. research to the Faculty of Automation, Electronics, and Computer Science.}
%------------------------------------------------
\entry
{2009}
{Poster}
{11th Int'l Conference on Heat Exchanger Fouling and Cleaning }
{Presented the paper \emph{Detection of Fouling in a Cross-Flow Heat Exchanger Using Wavelets}, Schladming, Austria.}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{2009}
{Presentation }
{University of Valenciennes and Hainaut-Cambresis, Valenciennes, France}
{As part of the collaboration with Sylvan Lalot, I presented the research faculty at the ENSIAME department at UVHC.}
%------------------------------------------------
\end{entrylist}
\section{grants}
%-------------------------------------------------------------------------------
%	GRANTS SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}
    %------------------------------------------------
    \entry
    {2012}
    {Grant for Teaching Development}
    {Univeristy of Iceland, Kennslumálasjóður}
    {Received a grant to improve undergraduate homework assignments in Engineering and Natural Sciences. Worked with the faculties to develop a new, simplified teaching method to reduce the workload for teachers while providing effective feedback for students. Due to work commitments, allowed co-grantee to use the grant to implement the new method.  }
    %------------------------------------------------
    \entry
    {2009-2012}
    {Postgraduate Scholarship}
    {University of Iceland Research Fund}
    {Three year stipend for doctoral studies.}
    %------------------------------------------------
    \entry
    {2010}
    {Mobility grant}
    {Fundusz Stypendialny i Szkoleniowy 
        \href{http://www.fss.org.pl/en/about}{(FSS)}} % (e. Scholarship and 
    %training fund between Iceland, Liechtenstein, Norway and Poland)}
    {Mobility grant to visit Silisian University, Gliwice, Poland.}
    %------------------------------------------------
    \entry
    {2009}
    {Postgraduate Scholarship}
    {French Embassy}
    {Awarded to Icelandic students pursuing a Masters degree in France.}
    %------------------------------------------------
\end{entrylist}

\section{extracurricular activity}
%-------------------------------------------------------------------------------
%	EXTRACURRICULAR ACTIVITY SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}

    %------------------------------------------------
    \vspace{-9pt}
    \entry{2018-2021}{Board member of Company Union}{deCODE Genetics}{}\vspace{-9pt}
    %------------------------------------------------
    \entry{2016}{Treasurer of Company Union}{AGR Dynamics}{}\vspace{-9pt}
    %------------------------------------------------
    \entry{2014-2015}{Treasurer of Company Union}{Valka}{}\vspace{-9pt}
    %------------------------------------------------    
    \entry{2011-2012}{Science Committee Member}{SENS, UI}{Served as a graduate student representative on the Science Committee at the University of Iceland, which aimed to enhance research activities and facilitate discussions on research in different fields of study.\vspace{6pt}
    }
    %------------------------------------------------
    \entry{2009-2011}{Co-founder and Treasurer of Heron}{SENS, UI }{As a founding member of the Heron Student Union, I played a key role in creating an organization that represented all postgraduate engineering and natural sciences students at the University of Iceland. I was instrumental in merging several defunct student organizations into a single entity and took on the responsibilities of managing the finances as treasurer.}
    %------------------------------------------------
    \entry{2009-2010}{Treasurer of BEST Reykjavik}{Board 
    of European Students of Technology (\href{https://www.best.eu.org/}{BEST})}{
    Represented BEST  Reykjavik at the BEST General Assembly. Organized two academic courses at the University of Iceland, hosting and entertaining 20 European students for a week.
    }
    %------------------------------------------------
    \entry{2006-2007}{President of Stigull}{SENS, UI}{Led the undergraduate student organization for Mathematics and Physics at UI.}
    %------------------------------------------------
\end{entrylist}

\section{awards}
%-------------------------------------------------------------------------------
%	AWARDS SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}
	%------------------------------------------------
	\entry
	{2015}
	{Nominated for Best Paper award}
	{9th Int'l Conference on Learning and Intelligent Optimization}
	{My paper \citetitle{InRu15a} was one of three full-paper submissions nominated for the Best Paper award.}
	%------------------------------------------------
	\entry
	{2005}
	{Magna cum laude}
	{The Commercial College of Iceland, Reykavik, Iceland}
	{Ranked in the top third of my graduating class and awarded for academic achievement during my final year of a Baccalaureate degree.}
	%------------------------------------------------
\end{entrylist}

\section{publications}
%-------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-------------------------------------------------------------------------------

{Literature available on 
\href{https://www.researchgate.net/profile/Helga_Ingimundardottir}{{\boldfont 
Research Gate}}}
\nocite{*}

%\printbibliography[type=misc, title={asdf}, heading=subbibliography]
\printbibsection{book}{thesis} 
\printbibsection{article}{article in peer-reviewed journals} 
\printbibsection{inproceedings}{international peer-reviewed conferences/proceedings} 
\printbibliography[type=misc, title={seminars}, heading=subbibliography]


%-------------------------------------------------------------------------------

\end{document}
