\section{membership in committees and unions}
\begin{entrylist}
\entry
{2015, 2023--}
{Seasonal Advisor for Technology Development Fund}
{Rannsóknamiðstöð Íslands (\href{https://www.rannis.is/}{Rannís})}
{
I served on the advisory board for grant applications to the Technology Development Fund at Rannís in 2015 and provided valuable insights on the selection of R\&D projects for technological development and innovation in Iceland. 
I resumed my role as an advisor in 2023.
}
%------------------------------------------------
\entry{2018-21}{Board member of Company Union}{deCODE Genetics}{\vspace{-9pt}}
%------------------------------------------------
\entry{2016}{Treasurer of Company Union}{AGR Dynamics}{\vspace{-9pt}}
%------------------------------------------------
\entry{2014-15}{Treasurer of Company Union}{Valka}{\vspace{-9pt}}
%------------------------------------------------    
\entry{2011-12}{Science Committee Member}{SENS, University of Iceland}{
Served as a graduate student representative on the Science Committee at the University of Iceland, which aimed to enhance research activities and facilitate discussions on research in different fields of study.
\vspace{6pt}
}
%------------------------------------------------
\entry{2009-11}{Co-founder and Treasurer of Heron}{SENS, University of Iceland}{
As a founding member of the Heron Student Union, I played a key role in creating an organization that represented all postgraduate engineering and natural sciences students at the University of Iceland. I was instrumental in merging several defunct student organizations into a single entity and took on the responsibilities of managing the finances as treasurer.
}
%------------------------------------------------
\entry{2009-10}{Treasurer of BEST Reykjavik}{Board of European Students of Technology (\href{https://www.best.eu.org/}{BEST})}{
Represented BEST  Reykjavik at the BEST General Assembly. Organized two academic courses at the University of Iceland, hosting and entertaining 20 European students for a week.
}
%------------------------------------------------
\entry{2006-7}{President of Stigull}{SENS, University of Iceland}{Led the undergraduate student organization for Mathematics and Physics at University of Iceland.}
\end{entrylist}
