\section{education}
\begin{entrylist}
\entry
{2009-16}
{Ph.D. {\normalfont of Computational Engineering}}
{The University of Iceland, Reykjavik}
{Conducted research on hyperheuristics with guidance from Prof. Tómas Philip Rúnarsson. Focused on automating the scheduling process for Job Shop Scheduling Problems using ordinal regression and analyzed the ``problem difficulty'' and ``algorithm's footprints in instance space'' for such optimization problems. Awarded a doctoral grant from the University of Iceland Research Fund. \\
{\boldfont Thesis:} \citetitle{phd-thesis}. 
Available at \url{http://hdl.handle.net/1946/25337}.}
%------------------------------------------------
\entry
{2010-12}
{Postgraduate Diploma {\normalfont of School of Education}}
{The University of Iceland, Reykjavik}
{A 30 ECTS program spearheaded by Professor Guðrún Geirsdóttir, specifically tailored for faculty members and doctoral students teaching at the University of Iceland. As one of the inaugural participants in 2010, I completed courses over three semesters, focusing on university-level teaching studies, course design and assessment, and reflective practice and professional development. Significantly, the program's impact was exemplified in the final class, where I wrote and successfully obtained a grant application from the \textit{University of Iceland Teaching Fund} based on my coursework accomplishments.}
%------------------------------------------------
\entry
{2008-10}
{Masters {\normalfont of Computational Engineering}}
{The University of Iceland, Reykjavik}
{Conducted research with Prof. Sylvain Lalot at the University of Valenciennes and Hainaut-Cambresis in Valenciennes, France. Explored the feasibility of using wavelet transforms to detect fouling in cross-flow heat exchangers using measurements obtained during normal operation.
Awarded a grant from the Icelandic French Embassy to study in France. \\	
{\boldfont Thesis:} \citetitle{msc-thesis}. 
Available at \url{http://hdl.handle.net/1946/4445}.}
%------------------------------------------------
\entry
{2005-08}
{Bachelor {\normalfont of Mathematics}}
{The University of Iceland, Reykjavik}
{Specialization in Computer Science}
%------------------------------------------------
\end{entrylist}
