\section{grants}
\begin{entrylist}
\entry
{2024}
{Higher Education Mobility Grant}
{ERASMUS+}
{This mobility aims to enhance University of Iceland's teaching methodologies by learning
from Aalborg University's project-based learning and Denmarks Techncial University's curriculum
integration. The collaboration will improve UoI's curriculum, facilitate BSc to MSc transitions,
and strengthen international partnerships.}
\entry
{2024}
{Grant for Student Funding}
{The Icelandic Centre for Research, Student Innovation Fund}
{
As part of the \emph{HiDef Textiles} project, received funding to update a 90s knitting machine to
modern standards. This involves employing three bachelor's graduates for three months each. The
project combines sustainable technology, textile innovation, STEAM education, AI, and IoT.
Project aims to merge tradition with digital advancements, creating tools for modern users and
teaching technical literacy innovatively. By summer's end, a functional knitting machine will be
ready for presentations at local conferences.
URL: \url{https://sjodir.rannis.is/gagnatorg/app_details.php?id=12387&fund=11&eid=5628}
}
%------------------------------------------------
\entry
{2024-26}
{Project Grant: HiDef Textiles: Optimizing Textile Processes with AI}
{University of Iceland Research Fund}
{This research project merges AI, industrial engineering, computer science, and textile
craftsmanship to enhance various textile processes. Our goal is to democratize technology and
programming through textiles, integrating arts and sciences. We are developing a sustainable
learning platform to share industrial best practices, emphasizing women's participation in STEM.
Funding supports this STEAM approach, fostering an inclusive community and innovation culture.
}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{2012}
{Grant for Teaching Development}
{Univeristy of Iceland, Academic Affairs Fund}
{Received a grant for 800,000 ISK to improve undergraduate homework assignments in Engineering
and Natural Sciences, titled \emph{Breytt dæmatímafyrirkomulag hjá VON}. Worked with the
faculties to develop a new, simplified teaching method to reduce the workload for teachers while
providing effective feedback for students. Due to work commitments, allowed co-grantee to use the
grant to implement the new method. Work done as part of the course \textit{Reflective practice
and professional development} during my graduate diploma in Teaching Studies in Higher Education.
URL: \url{https://www.hi.is/sites/default/files/ame18/HaskolaradsfundirPDF/kennslumsjodur_2012_uthlutunarlisti.pdf}
}
%------------------------------------------------
\entry
{2009-12}
{Postgraduate Scholarship}
{University of Iceland Research Fund}
{Three year stipend for doctoral studies.}
%------------------------------------------------
\entry
{2010}
{Higher Education Mobility Grant}
{Fundusz Stypendialny i Szkoleniowy (FSS)} 
% (e. Scholarship and training fund between Iceland, Liechtenstein, Norway and Poland)}
{Mobility grant for students and university staff to visit Silisian University, Gliwice, Poland.}
%------------------------------------------------
\entry
{2009}
{Postgraduate Scholarship}
{French Embassy, Reykjavík Iceland}
{Awarded to Icelandic students pursuing a Masters degree in France.}
%------------------------------------------------
\end{entrylist}
