\section{work experience}
\begin{entrylist}
\entry
{2022--23}
{Travelshift}
{Reykjavik, Iceland}
{\emph{Head of AI research} at \href{https://www.travelshift.com/}{Travelshift}.\\
As the leader of an AI research team, I developed and implemented data-driven approaches to optimize travel plans for vacation packages offered on \href{www.guidetoeurope.com}{GuideTo\-Europe.com}. Our project focused on the NP-hard optimization problem of the traveling thief, which combines the concepts of the knapsack problem and the traveling salesman problem. 
In addition, I worked on patent applications related to our research.
I ensured that the optimized travel plans met stakeholders' requirements by designing and implementing AI algorithms, analyzing data, collaborating with other teams, and staying up-to-date with AI research trends and advancements.}
%------------------------------------------------
\entry
{2021-22}
{CCP Games}
{Reykjavik, Iceland}
{\emph{Data Scientist} for \href{https://www.ccpgames.com/}{CCP Games}' data department.\\
I played a leading role in the development of a recommendation engine service for new characters in EVE Online, working alongside other partners. My responsibilities included creating real-time time-series features based on proto-events from Kafka streams, using the TimescaleDB extension for pgSQL functions for feature engineering. Additionally, I developed ad-hoc metrics to measure content quality and engagement for these new recommendation models.
}
%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{2016-21}
{deCODE Genetics}
{Reykjavik, Iceland}
{\emph{Research Scientist} for \href{https://www.decode.com/}{deCODE}'s statistical department.\\
I was a founding member of a dedicated Oxford Nanopore Technologies (ONT) team at deCODE Genetics, responsible for implementing and maintaining the long range sequencing analysis pipeline. In this role, I collaborated closely with the lab department to determine protocols, and worked with the IT department to make necessary changes to cluster and disk architecture to efficiently process a large amount of data (6 petabytes over 3 years), ensuring data integrity. Additionally, I played a key role in writing research papers with the ONT team, and was responsible for operationalizing research findings for use in production environments.
}
%------------------------------------------------
\entry
{2015-16}
{AGR Dynamics}
{Reykjavik, Iceland}
{\emph{SQL Consultant} for \href{http://agrdynamics.com/}{AGR~5}\\
I provided customized solutions for AGR~5, a web-based supply chain management system that enables users to visualize sales history and generate order proposals using statistical forecasting. My work involved implementing AGR~5 to companies' ERP systems, maintaining databases, and developing custom SQL solutions to meet individual customer needs.
}    
%------------------------------------------------
\entry
{2013-15}
{Valka}
{Kopavogur, Iceland}
{\emph{Computational Engineer} in Research and Development \\
As a full-time researcher at Valka, a leading provider of equipment and automation solutions for the fish processing industry, I played a crucial role in several important accomplishments. These include designing and implementing an intelligent fish portioning algorithm based on X-Ray imagery, generalizing the fish bone detection algorithm for multiple species with fast and accurate calculations, collaborating on three-dimensional visualizations of fish bones, and conducting efficiency tests and preparing reports. Through these achievements, I helped to contribute to Valka's success in delivering innovative solutions to the industry.
}
%------------------------------------------------
\entry
{2007-9}
{Landsbankinn}
{Reykjavik, Iceland}
{\emph{Summer Intern} at: Testing Department in 2009; Quantitative Research and Trading Support for the FX and Derivatives Sales in 2008; and at Business Support in 2007.}
\end{entrylist}
